\documentclass[11pt,a4paper]{letter}

\usepackage[scale=0.8]{geometry}
\usepackage{hyperref}

\newcommand{\Company}{Cresta}
\newcommand{\Position}{AI Quality Assurance Intern}
\newcommand{\WhyCompany}{At \Company}

\signature{Leo Wu}
\address{2438-89 Chestnut St, Toronto, ON, Canada}

\begin{document}
\begin{letter}{}
  \opening{Dear \Company\ Recruitment Team:}

  I am writing to apply for the \Position\ position at \Company. As a first-year student intending to major in Statistics and Computer Science at the University of Toronto, I have extensive experience in full-stack web development, applied machine learning, and collaborative tools for software development. \WhyCompany, and I am ready to contribute to your engineering team by applying my technical skills to real-world, high-impact projects.

  As a member of the University of Toronto Autonomous Scale Racing (UTASR) team, I combined research and application by implementing the state-of-the-art Deeplabv3 segmentation model using PyTorch to enhance autonomous vehicle perception. This experience deepened my appreciation for building systems that strike a balance between accuracy and performance, as well as the importance of using version control systems effectively to support cohesive teamwork.

  In the University of Toronto BIONIC Club, I currently lead the software development of an Android app for a client with special accessibility needs. Moving out of my usual comfort zone of React Native to Kotlin-based, native Android development pushed me to be extra attentive to all parts of the project - a challenge that strengthened both my technical skills and communication skills as a lead.

  Beyond university work, I enjoy sharpening my skills through personal projects. I built \href{https://lerna.app}{Lerna} and \href{https://commonblog.vercel.app}{CommonBlog}, which gave me hands-on experience in full-stack web development from initial commit to deployment. From using new technologies such as PostgreSQL to designing fault-tolerant APIs, I've learned to treat software development as an invaluable opportunity to challenge myself while delivering reliable products for users.

  I am incredibly excited to bring my curiosity, technical foundations, and collaborative mindset to \Company. Thank you for considering my application.

  \closing{Sincerely,}
\end{letter}
\end{document}
