\documentclass{letter}
\usepackage{hyperref}

\signature{Hanbang Wu}
\address{2438-89 Chestnut St, Toronto, ON, Canada}

\begin{document}
\begin{letter}{
    Eunice Eunhee Jang\\
    Ontario Institute for Studies in Education
  }

  \opening{Dear Professor Jang,}

  I am writing to apply for the Research Assistant position for the  BalanceAI and APLUS projects at OISE. As a first-year UTSG student, I am eager to contribute my programming skills to these exciting initiatives at the intersection of technology and education.

  In high school, I developed a solid foundation in programming. My primary interest is web development. A key project is Lerna (\href{https://lerna.app}{https://lerna.app}), a compilation of interactive notes using Next.js (a React framework). The website has been my focus since grade 10, and it is the culmination of countless hours of UI optimization, content creation, and my relentless learning about web development (and wrestling with Git, too). Last summer, I challenged myself to learn database technologies and integrate them into a website. Thus, I created CommonBlog (\href{commonblog.vercel.app}{commonblog.vercel.app}), which merges my React experience with PostgreSQL (hosted on Supabase), complete with a full-fledged user authentication system built on Supabase Auth. This project gave me substantial experience with relational databases and also invigorated my excitement in learning NoSQL and MongoDB.

  These experiences have not only deepened my technical proficiency but also fuelled my interest in continuing further. While I'm proud of my projects, their development has been experimental and self-taught. What excites me the most about this position is the opportunity to work with and learn from an experienced, professional team to validate my current skills, refine my practices, and create impact with my work. I am confident that my enthusiasm, technical foundations, and eagerness to grow and learn will make me an invaluable member of your team.

  Thank you so much for your time and consideration. I would be delighted to discuss with you on how background and enthusiasm can contribute to the success of these projects.

  \closing{Sincerely,}
\end{letter}
\end{document}
