\documentclass{letter}
\usepackage{hyperref}

\signature{Hanbang Wu}
\address{2438-89 Chestnut St, Toronto, ON, Canada}
\date{September 21, 2025}

\begin{document}
\begin{letter}{
    Blair Armstrong\\
    Computation and Psycholinguistics Laboratory\\
    University of Toronto Scarborough
  }

  \opening{Dear Professor Armstrong,}

  I am writing to apply for the Lab Programmer position at the Computation and Psycholinguistics Laboratory. As a first-year UTSG student, I am eager to contribute my programming skills to research at the intersection of technology and cognitive sciences.

  In high school, I developed a solid foundation in programming, with a particular focus on web development. A key project is Lerna (\href{https://lerna.app}{lerna.app}), a compilation of interactive notes using React. It has been my focus since grade 10, and it has given me extensive experience in debugging and troubleshooting code, adapting to new technologies, and using Git. More recently, I created CommonBlog (\href{https://commonblog.vercel.app}{commonblog.vercel.app}), which uses PostgreSQL and features a full-fledged user authentication system. I am also proficient in Python, having worked on a command-line-based website categorizer that leverages the power of Google Gemma 3 in intelligently processing website content.

  What excites me most about this position is the chance to contribute to interdisciplinary projects that bridge psychology, linguistics, and programming. I am confident that my enthusiasm, technical foundations, and eagerness to grow and learn will make me an invaluable member of the CAP Lab team.

  Thank you so much for your time and consideration. I would be delighted to discuss with you on how background and enthusiasm can contribute to the success of these projects.

  \closing{Sincerely,}
\end{letter}
\end{document}