\documentclass{letter}
\usepackage{hyperref}

\signature{Hanbang Wu}
\address{2438-89 Chestnut St, Toronto, ON, Canada}

\begin{document}
\begin{letter}{
    Mark Chignell\\
    Faculty of Applied Science \& Engineering (Interactive Media Lab)
  }

  \opening{Dear Professor Chignell:}

  I am writing to apply for the React Game Researcher position at the Interactive Media Lab. As a first-year UTSG student, I am eager to contribute my programming skills to these exciting initiatives at the intersection of technology and gaming.

  In high school, I developed a solid foundation in programming. My primary interest is web development. A key project is Lerna (\href{https://lerna.app}{https://lerna.app}), a compilation of interactive notes using Next.js (a React framework). The website has been my focus since grade 10, and it is the culmination of countless hours of UI optimization, content creation, and my relentless learning about web development (and wrestling with Git, too). Last summer, I challenged myself to learn database technologies and integrate them into a website. Thus, I created CommonBlog (\href{https://commonblog.vercel.app}{https://commonblog.vercel.app}), which merges my React experience with PostgreSQL (hosted on Supabase), complete with a full-fledged user authentication system built on Supabase Auth. This project gave me substantial experience with relational databases and also invigorated my excitement in learning NoSQL and MongoDB.

  These experiences have not only deepened my technical proficiency but also fuelled my interest in continuing further. While my background is primarily in the web, I am especially excited for this position because it gives me the opportunity to apply my experience in React in a whole new domain and support research that promotes the health and well-being of older adults, which I understand is one of the missions of the Interactive Media Lab. I am eager to expand my capabilities, work with, and learn from an experienced team and am confident that my enthusiasm, technical foundations, and eagerness to grow and learn will make me an invaluable member of the team.

  Thank you so much for your time and consideration. I would be delighted to discuss with you on how background and enthusiasm can contribute to the success of the lab's projects and research.

  \closing{Sincerely,}
\end{letter}
\end{document}
