\documentclass{letter}
\usepackage{hyperref}

\signature{Leo Wu}
\address{1121 Edinburgh St, New Westminster, BC, Canada}

\begin{document}
\begin{letter}{}

  \opening{Dear Electronic Arts Recruitment Team:}

  I am writing to apply for the 2026 AI Engineer Intern position at Electronic Arts. As a first-year student in statistics and computer science at the University of Toronto, with experience in machine learning tools such as PyTorch, scikit-learn, Numpy, Pandas, and version control systems, I am ready to contribute and learn in Electronic Arts' challenging yet enriching work environment.

  As a Machine Learning Engineer at the University of Toronto Autonomous Scale Racing team, I am working on implementing the Deeplabv3 segmentation model with PyTorch and contributed to control logic design for autonomous driving. The hands-on experience of not only writing code but also collaborating with others gave me invaluable experience that I hope to utilize as an intern at Robinhood.

  As part of the University of Toronto Bioengineering Innovation and Outreach in Consulting Club (UT BIONIC), I am developing a Kotlin Android app integrated with Google Assistant and ESP32 customized for our client, who have accessibility needs. While my expertise lies in React Native, I decided to challenge myself and the mobile app team to take on Kotlin as it would ensure the greatest reliability and compatibility, which are our two main concerns.

  Outside of school, I enjoy challenging myself through personal projects. I started \href{https://lerna.app}{Lerna} in grade 10, which became my first interaction with Next.js, Node.js, and Vercel. Last summer, I learned the ways of databases like PostgreSQL through \href{https://commonblog.vercel.app}{CommonBlog}, which I implemented using Prisma and Supabase.

  Thank you very much for considering my application. I would be thrilled to contribute my skills and enthusiasm to Electronic Arts this summer.
  \closing{Sincerely,}
\end{letter}
\end{document}
