\documentclass{letter}
\usepackage{hyperref}

\signature{Leo Wu}
\address{2438-89 Chestnut St, Toronto, ON, Canada}

\begin{document}
\begin{letter}{}

  \opening{Dear MongoDB Early Talent Recruitment Team:}

  I am writing to apply for the 2026 Software Engineering Intern position at MongoDB, Toronto. As a first-year student in statistics and computer science at the University of Toronto, with extensive experience in full-stack web development, machine learning, and version control systems, I am ready to contribute and learn in MongoDB's challenging yet enriching work environment.

  As a Machine Learning Engineer at the University of Toronto Autonomous Scale Racing team, I am working on implementing the Deeplabv3 segmentation model with PyTorch and contributed to control logic design for autonomous driving. The hands-on experience of not only writing code but also collaborating with others gave me invaluable experience that I hope to utilize as an intern at MongoDB.

  As part of the University of Toronto Bioengineering Innovation and Outreach in Consulting Club (UT BIONIC), I am developing a Kotlin Android app integrated with Google Assistant and ESP32 customized for our client, who have accessibility needs. While my expertise lies in React Native, I decided to challenge myself and the mobile app team to take on Kotlin as it would ensure the greatest reliability and compatibility, which are our two main concerns.

  Outside of school, I enjoy challenging myself through personal projects. I started \href{https://lerna.app}{Lerna} in grade 10, which became my first interaction with Next.js, Node.js, and Vercel. Last summer, I learned the ways of databases like PostgreSQL through \href{https://commonblog.vercel.app}{CommonBlog}, which I implemented using Prisma and Supabase.

  I am incredibly eager to put my skills to the test in a rewarding work environment like that of MongoDB, where I hope to work alongside experienced engineers in learning the ways of delivering production-grade code and working in a large team.

  Thank you very much for considering my application. I would be thrilled to contribute my skills and enthusiasm to MongoDB this summer.
  \closing{Sincerely,}
\end{letter}
\end{document}

% Why are you interested in this role at MongoDB?
% I am eager to work at MongoDB because it would allow me to see, for the first time, how serious code is produced from beginning to finish for products as complex as those of MongoDB. I want to see how a seasoned software engineer would quash a pesky bug in JavaScript, or how a machine learning engineer would overcome the model performance bottlenecks in a production setting. More than anything, I'm excited for the opportunity to move beyond coding alone in my room to a dynamic and challenging environment with a team.
