% name="CV.tex" && latexindent -w $name && pdflatex $name && rm *.bak* *.log *.aux *.log
\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\setlength{\parindent}{0pt}

\title{\textbf{Curriculum Vitae}}
\author{Leo Duan}
\date{}

\begin{document}

\maketitle

\section*{Basic Information}

\textbf{Name:} Leo Duan

\textbf{Phone number:} 604-928-8182

\textbf{Email:} leoduan0@icloud.com

\textbf{Website:} leoduan.com

\section*{Education}

\begin{itemize}
	\item New Westminster Secondary School - 2025 (expected)
\end{itemize}

\subsection*{Courses and Exams}

\subsubsection*{International Baccalaureate (IB)}

\begin{itemize}
	\item IB Analysis \& Approaches HL
	\item IB Physics HL
	\item IB Chemistry HL
	\item IB Literature HL
	\item IB Psychology SL
	\item IB Spanish (ab initio) SL
\end{itemize}

\subsubsection*{Advanced Placement (AP)}

\begin{itemize}
	\item AP Physics 1: 5
	\item AP Physics 2: 5
	\item AP Physics C Mechanics: 5
	\item AP Physics C Electricity and Magnetism: 5
	\item AP Chemistry: 5
	\item AP Calculus BC: 5 (AP Calculus AB subscore: 5)
\end{itemize}

\subsubsection*{SAT}

\begin{itemize}
	\item Total score: 1550
	\item Evidence-based reading and writing score: 750
	\item Math score: 800
\end{itemize}

\section*{Projects}

\begin{itemize}
	\item \textbf{leoduan.com} - Personal website. Built with Next.js and TypeScript.
	\item \textbf{Lerna (lerna.app)} - Educational platform. Built with Next.js, TypeScript, MDX, Python (PyLaTeX), and LaTeX.
	\item \textbf{GPQ (gpq.vercel.app)} - Acronym for ``Grind Practice Questions''. Question bank for the digital SAT. Built with Next.js, TypeScript, and MDX.
	\item \textbf{FiddleLeaf (fiddleleaf.vercel.app)} - A music transcription library. Built with Next.js and TypeScript. Scores created using MuseScore.
\end{itemize}

\section*{Work Experiences}

\subsection*{Cook, A\&W Restaurants; New Westminster, BC — 2022-07-11 to 2022-10-29}

\begin{itemize}
	\item Worked full time (40 hours) during summer break; most of the times until store closing at 12:30AM.
	\item Worked part time (20 hours) during school year.
	\item Operated clamshell grills, fryers, toasters, CVaps, and Thermodynes.
	\item Made orders on demand while following the standard operating procedure.
	\item Trained on A\&W standards and WHMIS.
	\item Worked cooperatively with a team or independently in the operation of the kitchen.
\end{itemize}

% \subsection*{Co-owner, Facebook Marketplace Account; New Westminster, BC — 2021-10 to 2022-12}

% \begin{itemize}
%     \item Generated more than \$3000 in total revenue with 94 completed orders.
%     \item Communicated with customers both in person and online.
%     \item Cooperated with partner in maintaining the account.
%     \item Delivered products to customers by commuting and using mailing services.
%     \item Performed accounting, product record, and price record for transactions using Apple Numbers.
% \end{itemize}

\subsection*{Packer, Roger's Custom Meats (1981) LTD; Prince George, BC — 2019-01 to 2020-03}

\begin{itemize}
	\item Labelled products with pricing guns and labelling machines.
	\item Operated of vacuum sealers, scales, and plastic film machines.
	\item Boxed items according to purchase order.
\end{itemize}

\subsection*{Go Tutor; Prince George, BC — 2018-04 to 2018-09}

\begin{itemize}
	\item Tutored the board game of Go
\end{itemize}

\section*{Achievements}

\begin{itemize}
	\item Honourable Mention at the Toshiba ExploraVision Science Competition - 2024
	\item Played trumpet in the school Shrek the Musical production, which won 1st place at the Canada Young Theatre Awards - 2024
	\item 4th place out of 78 teams at the 46th UBC Physics Olympics Quizzics - 2024
	\item Participated in the Physics Brawl — 2023
	\item Participated in the Kwantlen Science Challenge — 2023
	\item Highly Commended in Minds Underground Essay Competition — 2023
	\item Participated in the Breakthrough Junior Challenge — 2021, 2022
	\item Represented school in school team and our teams won the Innovation Project Award and the Motivate Award in the FIRST Lego League Challenge in Victoria, BC — 2020
	\item 2nd place in Red Cedar Book Awards Competition — 2020
	\item Canadian Red Cross Babysitter Certificate — 2019
	\item Canadian Red Cross Level 4 Swimming Certificate — 2018
	\item 2 gold medals, 1 silver medal in Go Championship in Shenyang, China — 2015, 2016
\end{itemize}

\section*{Extracurriculars}

\subsection*{Science}

\begin{itemize}
	\item Physics Club - President. Club dedicated to helping avid physics students in sharpening their physics skills and preparing for competitions.
	\item Science Club - Co-president. Participated in the school team for Kwantlen Science Challenge and the 46th UBC Physics Olympics.
\end{itemize}

\subsection*{Music}

\begin{itemize}
	\item Vancouver Youth Jazz Orchestra - Trumpeter. Played at the Vancouver International Jazz Festival 2024.
	\item Jam Club - Founder, president, trumpeter, arranger. Just a jazz club!
	\item Shrek the Musical (school production) - Trumpeter
	\item New Westminster Youth Jazz Combo - Pianist, arranger.
	\item New Westminster Secondary School Jazz Band (A and B) - Trumpeter.
	\item Noxious Obs Marching Band - Trumpeter. Played at the New West Pride Street Festival 2023 and around the city on Halloween 2023.
\end{itemize}

\subsection*{Others}
\begin{itemize}
	% \item Writings (leoduan.com/writings) - Some personal writings of my ideas in philosophy and science.
	\item Schoolhouse (schoolhouse.world) - Tutor. Certified tutor in calculus, physics, and pre-algebra.
	\item Harvard Pre-College Summer School Program - Accepted, did not attend.
	\item Stanford Summer Session - Accepted, did not attend.
	\item Columbia Summer High School Academic Program for Engineers (SHAPE) - Accepted, did not attend.
	\item Indigenous Events Committee - Co-president. Helped out with Indigenous related events throughout the school. Funded more than \$700 for a food drive going to help roughly 30 families in need in a winter food drive.
	\item Volunteering for MP Peter Julian - Volunteer. Volunteered for MP Peter Julian in the 2023 July 1st event at New Westminster Pier Park.
\end{itemize}

\section*{Languages}

\begin{itemize}
	\item English (bilingual proficiency)
	\item Mandarin Chinese (native proficiency)
\end{itemize}

\end{document}
