\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

\setlength{\parindent}{0pt}

\title{\textbf{Resumé}}
\author{}
\date{}

\begin{document}

\maketitle

\section*{Basic Information}

\textbf{Name:} Hanbang Wu (preferred: Leo Duan)

\textbf{Phone number:} 604-928-8182

\textbf{Email:} leoduan0@icloud.com

\textbf{Website:} leoduan.com

\section*{Education}

\begin{tabular}{@{}ll}
	2021-2025 & IB Diploma, Dogwood Diploma - New Westminster Secondary School \\
\end{tabular}

\subsection*{International Baccalaureate (IB) Diploma Programme}

\begin{itemize}
	\item Analysis and Approaches HL: 7P
	\item Physics HL: 7P
	\item Chemistry HL: 7P
	\item Psychology SL: 7P
	\item English Literature A HL: 6P
	\item Spanish ab initio: 6P
	\item ToK/EE: 2P
	\item Total (with core): 42P/45
\end{itemize}

*P refers to predicted grades.

\subsection*{Advanced Placement (AP)}

\begin{itemize}
	\item Calculus BC (Calculus AB subscore: 5): 5
	\item Physics 1: 5
	\item Physics 2: 5
	\item Physics C: Mechanics: 5
	\item Physics C: Electricity and Magnetism: 5
	\item Chemistry: 5
\end{itemize}

\section*{Work Experience}

\subsection*{Cook, A\&W Restaurants; New Westminster, BC — 2022-07-11 to 2022-10-29}

\begin{itemize}
	\item Worked full-time (40 hours) during summer break; usually on closing shifts until 12:30 AM.
	\item Worked part-time (20 hours) during the school year.
	\item Operated clamshell grills, fryers, toasters, CVaps, and Thermodynes.
	\item Made orders on demand while following the standard operating procedures.
	\item Trained on A\&W standards and WHMIS.
	\item Worked cooperatively with a team or independently in kitchen operations.
\end{itemize}

\subsection*{Packer, Roger's Custom Meats (1981) LTD; Prince George, BC — 2019-01 to 2020-03}

\begin{itemize}
	\item Labelled products with pricing guns and labeling machines.
	\item Operated vacuum sealers, scales, and plastic film machines.
	\item Boxed items according to customer orders.
\end{itemize}

\subsection*{Go Tutor; Prince George, BC — 2018-04 to 2018-09}

\begin{itemize}
	\item Tutored student in the board game of Go
\end{itemize}

\section*{Projects}

\begin{itemize}
	\item \textbf{Personal website (leoduan.com)} - Personal website. Built with Next.js and TypeScript.
	\item \textbf{Lerna (www.lerna.app)} - Notes collection (mostly designed for IB) and STEM competition preparation platform. Built with Next.js, TypeScript, and \LaTeX with PyLaTeX.
	\item \textbf{Inka (www.inka.earth)} - Acronym for ``Inka's Not Khan Academy''. Question bank for the digital SAT and IB subjects. Collaborated with friends to create practice questions. Built with Next.js, TypeScript, and \LaTeX.
	\item \textbf{FiddleLeaf (fiddleleaf.vercel.app)} - A music transcription library. Built with Next.js and TypeScript. Created scores using MuseScore.
\end{itemize}

\section*{Achievements}

\begin{tabular}{@{}ll}
	2024       & Honorable Mention, Toshiba/NSTA ExploraVision                          \\
	2024       & 4th place (out of 78 teams), Quizzics at the 46th UBC Physics Olympics \\
	2023       & Highly Commended, Minds Underground Essay Competition in Mathematics   \\
	2020       & Strategy and Innovation Award and Rising Star Award, FIRST Lego League \\
	2020       & 2nd place, Battle of the Books                                         \\
	2015, 2016 & 2 gold medals and 1 silver medal, regional Go championship
\end{tabular}

\section*{Extracurriculars}

\subsection*{Science}

\begin{tabular}{@{}ll}
	2024      & Student - Quantum School for Young Students (University of Waterloo; online) \\
	2023-2024 & President - Physics Club                                                     \\
	2023-2025 & Member (11), President (12) - Science Club
\end{tabular}

\subsection*{Music}

\begin{tabular}{@{}ll}
	2024      & Trumpeter - Vancouver Youth Jazz Orchestra. Played at the Vancouver International Jazz Festival 2024. \\
	2023-2024 & Founder, president, trumpeter, arranger - Music Club. Played at the NWSS Jazz Night 2023.             \\
	2022-2023 & Trumpeter - Shrek the Musical                                                                         \\
	2021-2023 & Trumpeter - NWSS Jazz A and B                                                                         \\
	2022      & Trumpeter - Noxious Obs Marching Band
\end{tabular}

\subsection*{Others}

\begin{tabular}{@{}ll}
	2023-2024 & Co-president - Indigenous Events Committee
\end{tabular}

\section*{Languages}

\begin{itemize}
	\item English (speak, listen, read, write)
	\item Mandarin Chinese (speak, listen, read)
\end{itemize}

\end{document}

